Example Manuscript Template for a Data Analysis Project

### 2024-04-11 products/manuscript/Manuscript.qmd
Tidying stuff up and pushing the latest.
Tidying stuff up and pushing the latest.

```{r, echo=FALSE, message=FALSE}
data_location <- here::here("data","processed-data","flu_data_wide.rds")
flu_data_wide <- readRDS(data_location)

print(flu_data_wide)

@@

***Table 1:*** *World Flu Burden by Region Over the 2023-2024 Flu Season.*

@@

A cursory look at the data presented in **Figure 6** (above) shows a putative dependence of the AMR region flu season on the flu season peak approximately 3 week prior in the WPR region.  Likewise the peaks in reported flu cases in the EUR region seem to correspond to the WPR maxima approximately 3 weeks prior followed by a second maxima at a 3 week delay from the AMR region maxima.  A simple multiple linear regression allowing the EUR data to be dependent data, while using offset data from the WPR and AMR regions as independent data should reveal a strong relationship.

@@

@@

@tbl-summarytable shows a summary of the data.

Note the loading of the data providing a **relative** path using the `../../` notation. (Two dots means a folder up). You never want to specify an **absolute** path like `C:\ahandel\myproject\results\` because if you share this with someone, it won't work for them since they don't have that path. You can also use the `here` R package to create paths. See examples of that below. I generally recommend the `here` package.

```{r}
#| label: tbl-summarytable
#| tbl-cap: "Data summary table."
#| echo: FALSE
resulttable=readRDS("../../results/tables/summarytable.rds")
knitr::kable(resulttable)
```

***Table 1.*** \*

## Basic statistical analysis

*To get some further insight into your data, if reasonable you could compute simple statistics (e.g. simple models with 1 predictor) to look for associations between your outcome(s) and each individual predictor variable. Though note that unless you pre-specified the outcome and main exposure, any "p\<0.05 means statistical significance" interpretation is not valid.*

@fig-result shows a scatterplot figure produced by one of the R scripts.

```{r}
#| label: fig-result
#| fig-cap: "Height and weight stratified by gender."
#| echo: FALSE
knitr::include_graphics(here("results","figures","height-weight-stratified.png"))
```

@@

Example @tbl-resulttable2 shows a summary of a linear model fit.

```{r}
#| label: tbl-resulttable2
#| tbl-cap: "Linear model fit table."
#| echo: FALSE
resulttable2 = readRDS(here("results","tables","resulttable2.rds"))
knitr::kable(resulttable2)
```

@@

This paper [@leek2015] discusses types of analyses.

These papers [@mckay2020; @mckay2020a] are good examples of papers published using a fully reproducible setup similar to the one shown in this template.

Note that this cited reference will show up at the end of the document, the reference formatting is determined by the CSL file specified in the YAML header. Many more style files for almost any journal [are available](https://www.zotero.org/styles). You also specify the location of your bibtex reference file in the YAML. You can call your reference file anything you like.

>>>>

#| label: tbl-summary_flu_table
#| tbl-cap: "Reported Flu Cases for the 2023-2024 Seasn by WHO Region."
#| echo: FALSE
resulttable=readRDS("../../assets/flu_table_file.rds")
knitr::kable(resulttable)

@@

***Table 1:*** *World Flu Burden by Region Over the 2023-2024 Flu Season.*  The data is restricted to September 2023 through February 2024.

@@

# Basic statistical analysis:

A cursory look at the data presented in **Figure 6** (above) shows a putative dependence of the AMR region flu season on the flu season peak approximately 3 week prior in the WPR region.  Likewise the peaks in reported flu cases in the EUR region seem to correspond to the WPR maxima approximately 3 weeks prior followed by a second maxima at a 3 week delay from the AMR region maxima. An appropriate initial analysis would be to simply perform a linear regression of the data with the AMR and the EUR WHO regions being the dependent variables based on all other variables.  (See **Table 2** and **Table 3** below.) 
```{r, echo=FALSE, message=FALSE}
#| label: tbl-lmtableA
#| tbl-cap: ""
#| echo: FALSE
resulttable=readRDS("../../assets/lmtableA.rds")
knitr::kable(resulttable)

```
***Table 2:*** *Simple Linear Regression of AMR Dependent and All Other Variables as Independent.*

@@

#| label: tbl-lmtableA
#| tbl-cap: ""
#| echo: FALSE
resulttable=readRDS("../../assets/lmtableB.rds")
knitr::kable(resulttable)

```
***Table 3:*** *Simple Linear Regression of EUR Dependent and All Other Variables as Independent.*

From the results of the initial analysis, the data may create a better model if the data for each flu region were A simple multiple linear regression of the resulting data set allowing the EUR data to be dependent data, while using offset data from the WPR and AMR regions as independent data should reveal a strong relationship.  Once again, the easiest model to use for this analysis is a simple regression model.  The models should explore the dependence of current flu levels in the AMR and EUR WHO regions based on the levels of flu reported in the EMR, and WPR regions and the EMR, WPR, and AMR regions respectively.  If we consider that the trend may not be merely west to east, but that there may be feedback from the EUR region to the AMR region then another possible model would be the dependence of flu cases in the AMR region on cases in the later two regions.  (See **Table 4.**, **Table 5.**, and **Table 6.** below.)

#| label: tbl-lmtable1
#| tbl-cap: ""
#| echo: FALSE
resulttable=readRDS("../../assets/lmtable1.rds")
knitr::kable(resulttable)

```
***Table 4:*** *Simple Linear Regression of AMR Dependent with EMR and WPR as Independent Using Date Aligned Data.*

#| label: tbl-lmtable2
#| tbl-cap: ""
#| echo: FALSE
resulttable=readRDS("../../assets/lmtable2.rds")
knitr::kable(resulttable)

```
***Table 5:*** *Simple Linear Regression of EUR Dependent with EMR, WPR, and AMR as Independent Using Date Aligned Data.*

#| label: tbl-lmtable3
#| tbl-cap: ""
#| echo: FALSE
resulttable=readRDS("../../assets/lmtable3.rds")
knitr::kable(resulttable)

```
***Table 6:*** *Simple Linear Regression of AMR Dependent with EMR, WPR, and EUR as Independent Using Date Aligned Data*

```{r}

@@

```{r}

@@

```{r}

@@

### 2024-04-11 products/manuscript/workspace.qmd
Tidying stuff up and pushing the latest.
Tidying stuff up and pushing the latest.

@@

@@

*Explain anything related to your statistical analyses.*

>>>>

Flu_Tab_wide <- ggplot () + geom_blank() + labs(title = "Reported Flu Cases for the 2023-2024 Seasn by WHO Region.")

ggsave("Flu_Tab_wide.png", plot = Flu_Tab_wide, device = "png")

#Create the table.
summary_flu_tab = flu_data_wide <- monthly_summary2 %>% pivot_wider(names_from = MMWR, values_from = TOT_FLU)
print(summary_flu_tab)

# save to file
flu_table_file = here("assets", "flu_table_file.rds")
saveRDS(summary_flu_tab, file = flu_table_file)

@@

#These did not work worth a dang.

@@

*Explain anything related to your statistical analyses.*
```{r, echo=FALSE, message=FALSE}

suppressPackageStartupMessages(library(parsnip))
suppressPackageStartupMessages(library(tune))
suppressPackageStartupMessages(library(recipes))
suppressPackageStartupMessages(library(workflows))
suppressPackageStartupMessages(library(yardstick))
suppressPackageStartupMessages(library(rsample))

data_location <- here::here("data","raw-data","DATE_REGION.xlsx")
date_region <- readxl::read_excel(data_location)

date_region2 <- date_region %>% select(AFR, AMR, EMR, EUR, SEAR, WPR)

#AMR vs. ALL
lin_mod <- linear_reg() %>% set_engine("lm")
linfitA <- lin_mod %>% fit(AMR ~ ., data = date_region2)

tidy(linfitA)

# place results from fit into a data frame with the tidy function
lmtableA <- broom::tidy(linfitA)

#look at fit results
print(lmtableA)

# save fit results table  
table_fileA = here("assets", "lmtableA.rds")
saveRDS(lmtableA, file = table_fileA)

#EUR vs. ALL
lin_mod <- linear_reg() %>% set_engine("lm")
linfitB <- lin_mod %>% fit(EUR ~ ., data = date_region2)

tidy(linfitB)

# place results from fit into a data frame with the tidy function
lmtableB <- broom::tidy(linfitB)

#look at fit results
print(lmtableB)

# save fit results table  
table_fileB = here("assets", "lmtableB.rds")
saveRDS(lmtableB, file = table_fileB)

data_location <- here::here("data","raw-data","REGION_OFFSET.xlsx")
Region_offset <- readxl::read_excel(data_location)

print(Region_offset)

# fit the linear models with AMR as outcome 
# model has ALL OTHER REGIONS as predictors
lin_mod <- linear_reg() %>% set_engine("lm")
linfit1 <- lin_mod %>% fit(AMR ~ EMR + WPR, data = Region_offset)

#model 2 -- includes date variable
lin_mod <- linear_reg() %>% set_engine("lm")
linfit2 <- lin_mod %>% fit(EUR ~ EMR + WPR + AMR, data = Region_offset)

# Compute the RMSE and R squared for model 1
metrics_1 <- linfit1 %>% 
  predict(Region_offset) %>% 
  bind_cols(Region_offset) %>% 
  metrics(truth = AMR, estimate = .pred)

# Compute the RMSE and R squared for model 2
metrics_2 <- linfit2 %>% 
  predict(Region_offset) %>% 
  bind_cols(Region_offset) %>% 
  metrics(truth = EUR, estimate = .pred)

tidy(linfit1)
print(metrics_1)

# place results from fit into a data frame with the tidy function
lmtable1 <- broom::tidy(linfit1)

#look at fit results
print(lmtable1)

# save fit results table  
table_file1 = here("assets", "lmtable1.rds")
saveRDS(lmtable1, file = table_file1)

tidy(linfit2)
print(metrics_2)

# place results from fit into a data frame with the tidy function
lmtable2 <- broom::tidy(linfit2)

#look at fit results
print(lmtable2)

# save fit results table  
table_file2 = here("assets", "lmtable2.rds")
saveRDS(lmtable2, file = table_file2)

#model 3 -- includes date variable
lin_mod <- linear_reg() %>% set_engine("lm")
linfit3 <- lin_mod %>% fit(AMR ~ EMR +WPR + EUR, data = Region_offset)

# Compute the RMSE and R squared for model 3
metrics_3 <- linfit3 %>% 
  predict(Region_offset) %>% 
  bind_cols(Region_offset) %>% 
  metrics(truth = AMR, estimate = .pred)

tidy(linfit3)
print(metrics_3)

# place results from fit into a data frame with the tidy function
lmtable3 <- broom::tidy(linfit3)

#look at fit results
print(lmtable3)

# save fit results table  
table_file3 = here("assets", "lmtable3.rds")
saveRDS(lmtable3, file = table_file3)

lmfitB1 <- lm(EUR ~ WPR + AMR + EMR, Region_offset) 
lmtableB1 <- broom::tidy(lmfitB1)
print(lmtableB1)

logfitB1 <- glm(EUR ~ WPR + AMR + EMR, data = Region_offset)
logtableB1 <- broom::tidy(logfitB1)
print(logtableB1)

metrics_lm1 <- lmfitB1 %>% 
  predict(date_region2) %>% 
  bind_cols(date_region2) %>% 
  metrics(truth = EUR, estimate = .pred)

metrics_log1 <- logfitB1 %>% 
  predict(date_region2) %>% 
  bind_cols(date_region2) %>% 
  metrics(truth = EUR, estimate = .pred)

lmfitB2 <- lm(EUR ~ WPR + AMR + EMR, Region_offset) 
lmtableB1 <- broom::tidy(lmfitB1)
print(lmtableB1)

logfitB2 <- glm(EUR ~ WPR + AMR + EMR, data = Region_offset)
logtableB1 <- broom::tidy(logfitB1)
print(logtableB1)

## ---- model1 --------
set.seed(rngseed)
mod1 <- linear_reg(mode = "regression") %>% set_engine("lm")
wflow1 <- workflow() %>% 
  add_model(mod1) %>% 
  add_formula(Y ~ .)
fit1 <- wflow1 %>% fit(data = df1)

## ---- lasso-tuning --------
lasso_tune <- linear_reg(penalty = tune(), mixture = 1) %>%  set_engine("glmnet")

wflow_m2_t1 <- workflow() %>% 
  add_model(lasso_tune) %>% 
  add_formula(Y ~ .)

# make an object that one can use for tuning that's just the data
dfs <- apparent(df1)

# set up a grid of values to tune over
lasso_grid  <- tibble(penalty = 10^seq(-5, 2, length.out = 50))

lasso_tune <- tune_grid(
  wflow_m2_t1,
  resamples = dfs,
  grid = lasso_grid
)

# plot of performance
autoplot(lasso_tune, metric = "rmse")

# get best model
best_param <- select_best(lasso_tune, metric = "rmse")
best_lasso <- lasso_tune %>%
  filter_parameters(parameters = best_param) %>%
  collect_metrics()
print(best_lasso)
